A Data-Driven Framework for Neural Field Modeling

### 2011-01-06 ltx/first_order_framework/LaTeX_Manuscript.tex
minor chnages
minor edits

Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the left hand side} we get the approximation of the dynamic field

@@

The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}. \dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ become the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where

>>>>

Each connectivity basis function of the Mexican hat can, individually, be considered a layer in the Wilson and Cowan model. Rearranging the order of the spatial convolution in equation~\ref{DiscreteTimeModel} and substituting in equations~\ref{DefFieldDecomp} and~\ref{DefKernelDecomp} \dean{to the right hand side} we get the approximation of the dynamic field

@@

The analytic derivation of the inner product of \emph{n}-dimensional Gaussians, which was used for calculating $\mathbf\Gamma$, is provided in \ref{App:InnerProdOfGaussians}. \dean{Alternative field basis functions may be used to form the decomposition and if the basis is orthonormal then $\Gamma$ is simply the identity matrix.} Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the connectivity kernel basis functions where
